\input{courseLearningOutcomesAndCourseObjectives}
\newpage
\section * {Teaching Day Plan}

\begin{longtable}{ l  }
 \hline
    \\
    Day 01 MON Sept 14 \\ \\ 
     1. Evaluate software testing and quality assurance techniques as part of an integrated discipline of software quality verification and validation.\\
            1.1 Discuss the discipline of software engineering.\\
            1.2 Discuss the importance of software quality attributes.\\
            1.3 Analyze the software testing life-cycle.\\ \\
    \hline 
    \\         
    Day 02 TUE Sept 15 \\  \\ 
            2.1 Discuss the foundations of proper software properties, specifications and reliability versus safety. \\
            2.2 Analyze and compare examples of program verification and correctness. \\
		    Activity 1  6\% \\   \\   
    \hline 
    \\    Day 03 WED Sept 16 \\ \\ 
          2.3 Evaluate and determine courses of action taken from examples of failures, errors and faults. \\ \\ 
     \hline   
     \\       Day 04 THU Sept 17 \\    \\ 
        Review and reinforcement of topics covered so far: In class Review Activity \\
           2.4 Analyze methods related to software testing taxonomy. \\  \\ 
     \hline    
     \\        Day 05 FRI Sept 18 \\ \\ 
           3.1 Discuss test generation concepts. \\
             Activity 2  6\% \\ \\ 
      \newpage 
      \hline   
      
    \\          Day 06 MON Sept 21 \\ \\ 
            3.2 Analyze examples of functional criteria. \\
            Assignment 1  15\% \\ \\ 
      \hline   
     \\        Day 07 TUE Sept 22 \\ \\ 
         3.3 Analyze examples of structural criteria. \\
            Activity 3  6\% \\
           Test  1  20\%  \\ \\ 
      \hline   
    \\          Day 08 WED Sept 23 \\ \\ 
            4.1 Test oracle design specifications. \\
            4.2 Test driver design specifications. \\ \\ 
       \hline  
    \\         Day 09 THU Sept 24 \\ \\ 
            4.3 Test outcome analysis. \\ \\ 
       \hline  
    \\          Day 10 FRI Sept 25 \\ \\ 
            5.1 Discuss and anlayze examples of metrics for software testing. \\
            Activity 4  6\% \\ \\ 
      \hline   
    
    \\          Day 11 MON Sept 28 \\ \\ 
            5.2 Use software testing tools. \\
            Assignment 2 15\% \\ \\ 
      \hline   
    \\          Day 12 TUE Sept 29 \\ \\ 
            5.3 Analyze and test product lines. \\
            Activity 5  6\% \\ \\ 
    \hline     
    \\          Day 13 WED Sept 30 \\ \\ 
            Review and Reinforce All Topics \\
            Test  2 20\%  \\ \\ 
      
\end{longtable}
\newpage