\section{Learning Activity 2  Friday September 18}

\subsection{Scenario:}

]u have been Task by your manager with creating a training manual for your software company. This is a very common type of work activity you might find yourself doing as a new graduate your first job. New graduates are often assigned to do work involving assembling existing information, as they have not yet developed into role with specialized information which requires their focus, and tasks of this type will give you great exposure to the operation of the product and company which will be part of your training.
\\
Using Latex, you are To construct a training manual for the quality assurance team.

A complete rendition of this work will consist of the following elements:
\begin{itemize}
    \item Types of Bugs
    \item How they Occur   
    \item Where they occur: 
    \item What procedures and practices the team can do to prevent bugs from occurring. The best kind of bug is the one that never happened.
\end{itemize}
\\
Design a form which customers, developers, and test team members may use when they think they have encountered a bug in the product. Think through all the kinds of information you should capture, how should you prompt your users to document the bug so it can be reproduced by the test team, and how will you set up the workflow so this document may be moved from the person who creates it through to the test team and then to the information architect will close it.
\\
You may do this using any online technology are comfortable with. I suggest that Google sheets would be a simple and effective tool within which to create it. You will be making your own small-scale version of Bugzilla. In this way when we study Bugzilla, you will already have some ideas about what it should do and how it should do it.
\newline

Because this is a simulation and you don't have an actual company situation refer to, research and find three use cases of software failure. Using methods we have performed in classroom lectures, analyse the failure, describe the category of the failure, and discuss what you as the quality assurance lead in the team would've done to prevent that failure from occurring.
\\
\\

Remember our motto in this course which is that you cannot test your way out of a bad design. Testing is something that is baked into the structure of the product right from the first minutes that you begin to construct the software architecture.










